---
title: "Code_All"
author: "Rizal Mujahiddan"
date: "5/24/2022"
output: pdf_document
---

# Analysis Data with R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Library

```{r}
current_0 <- Sys.time()
library(tidyverse)
library(dplyr)
library(rpart)
library(rpart.plot)
library(caret)
library(caTools)
library(earth)
library(mda)
library(ROSE)
library(DataExplorer)
library(car)
library(randomForest)
```

## Import data from csv

```{r}
data <- read.csv("dataset.csv")
ukuran_data <- dim(data)
head_data <- head(data)
write.csv(head_data,"head_data.csv")
summary(data)
```

##  Handling Missing Value
### Check Table frequency NA
```{r}
# Check column if have NA's
kolom_NA <- data.frame(as.list(colSums(is.na(data))))
kolom_NA <- as.data.frame(t(kolom_NA))
kolom_NA <- data.frame(names = row.names(kolom_NA), kolom_NA)
rownames(kolom_NA) <- NULL
colnames(kolom_NA) <- c("Nama_Kolom","freq")

# pipelining https://raw.githubusercontent.com/rstudio/cheatsheets/main/data-transformation.pdf
kolom_NA <- kolom_NA %>% 
              mutate(percen_freq = freq / ukuran_data[1] * 100) %>% 
              filter(freq > 0)

kolom_NA
```

### delete Column

reference for deleting attribute in columns with threshold 10%:
  https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3701793/


```{r}
kolom_delete <- kolom_NA %>% filter(percen_freq > 10)
kolom_NA <- kolom_NA %>%
              filter(percen_freq <= 10)
data <- data %>% select(-c(kolom_delete$Nama_Kolom))
```


### Divide column by datatype with variable
```{r}
# pembagian kolom NA berdasarkan tipe data 
int_kat <- names(which(lapply(data[kolom_NA$Nama_Kolom],class) == "integer"))
flo_num <- names(which(lapply(data[kolom_NA$Nama_Kolom],class) == "numeric"))

kolom_NA_cat <- kolom_NA %>% filter(Nama_Kolom %in% int_kat) %>% select(Nama_Kolom)
kolom_NA_cat <- kolom_NA_cat$Nama_Kolom

kolom_NA_num <- kolom_NA %>% filter(Nama_Kolom %in% flo_num) %>% select(Nama_Kolom)
kolom_NA_num <- kolom_NA_num$Nama_Kolom
kolom_NA_num
```
```{r}
kolom_NA_cat
```
### median numeric imputation
```{r}
for(kolomku in kolom_NA_num){
  data[[kolomku]][is.na(data[[kolomku]])] = median(data[[kolomku]],na.rm=T)
}

kolom_NA_cat_factor <- c()
kolom_NA_cat_int <- c()
for(kolom in kolom_NA_cat){
  banyak_unique <- length(unique(data[[kolom]]))
  if(banyak_unique > 10){
    kolom_NA_cat_int <- c(kolom_NA_cat_int,kolom)
  } else{
    kolom_NA_cat_factor <- c(kolom_NA_cat_factor,kolom)
  }
}
kolom_NA_cat_factor
```
```{r}
kolom_NA_cat_int
```

### median integer imputation
```{r}
for(kolomku in kolom_NA_cat_int){
  data[[kolomku]][is.na(data[[kolomku]])] = median(data[[kolomku]],na.rm=T)
}
```

### mode factor imputation
```{r}
for(kolomku in kolom_NA_cat_factor){
  data[[kolomku]][is.na(data[[kolomku]])] = as.numeric(names(sort(-table(data[[kolomku]])))[1])
  data[[kolomku]] <- as.factor(data[[kolomku]])
}
```

### Selecting Feature (Deleting id) because dont dependending for evaluation.
```{r}
data <- data %>% select(-c(encounter_id,patient_id,
                           hospital_id,icu_id))
```

### Factorizing Dataset
```{r}
kol_char <- names(which(lapply(data,class)=="character"))

for(kol in kol_char){
  mode_impute <- names(sort(-table(data[[kol]])))[1]
   data[[kol]] <- replace(data[[kol]],data[[kol]]=="",mode_impute)
   data[[kol]] <- as.factor(data[[kol]])
}
head(data)
```
```{r}
data <- data %>%
mutate(hospital_death = case_when(hospital_death == 0 ~ 'Survived',
                                  hospital_death == 1 ~ 'Death'))
data$hospital_death <- factor(data$hospital_death,levels = c("Survived","Death"),labels = c("Survived","Death"))
str(data)
```

## feature engineering
### averaging dataset
```{r}
data$d1_diasbp <- (data$d1_diasbp_min + 
                     data$d1_diasbp_max)/2
data$d1_diasbp_noninvasive <- (data$d1_diasbp_noninvasive_min + 
                                 data$d1_diasbp_noninvasive_max)/2
data$d1_heartrate <- (data$d1_heartrate_min + 
                   data$d1_heartrate_max) / 2
data$d1_mbp <- (data$d1_mbp_max + data$d1_mbp_min)/2
data$d1_mbp_noninvasive <- (data$d1_mbp_noninvasive_max +
                            data$d1_mbp_noninvasive_min)/2
data$d1_glucose <- (data$d1_glucose_max + data$d1_glucose_min)/2
data$d1_resprate <- (data$d1_resprate_min + data$d1_resprate_max)/2
data$d1_sysbp <- (data$d1_sysbp_min + data$d1_sysbp_max)/2
data$d1_sysbp_noninvasive <- (data$d1_sysbp_noninvasive_max + 
                                data$d1_sysbp_noninvasive_min)/2
data$d1_temp <- (data$d1_temp_min + data$d1_temp_max)/2
data$h1_diasbp <- (data$h1_diasbp_max + data$h1_diasbp_min)/2
data$h1_diasbp_noninvasive <- (data$h1_diasbp_noninvasive_min + 
                                 data$h1_diasbp_noninvasive_max)/2
data$h1_heartrate <- (data$h1_heartrate_min  + data$h1_heartrate_max)/2
data$h1_mbp <- (data$h1_mbp_max + data$h1_mbp_min)/2
data$h1_mbp_noninvasive <- (data$h1_mbp_noninvasive_max + 
                              data$h1_mbp_noninvasive_min)/2
data$h1_resprate <- (data$h1_resprate_min + data$h1_resprate_max)
data$h1_spo2 <- (data$h1_spo2_min + data$h1_spo2_max)/2
data$h1_sysbp <- (data$h1_sysbp_max + data$h1_sysbp_min)/2
data$h1_sysbp_noninvasive <- (data$h1_sysbp_noninvasive_max + 
                                data$h1_diasbp_noninvasive_min)/2


data <- data %>% select(-c(d1_diasbp_min,d1_diasbp_max,
                          d1_diasbp_noninvasive_max,
                          d1_diasbp_noninvasive_min,
                          d1_glucose_max,d1_glucose_min,
                          d1_heartrate_max,d1_heartrate_min,
                          d1_mbp_max,d1_mbp_min,
                          d1_mbp_noninvasive_max,
                          d1_mbp_min,d1_resprate_min,
                          d1_resprate_max,
                          d1_spo2_max,d1_spo2_min,
                          d1_sysbp_max,d1_sysbp_min,
                          d1_sysbp_max,d1_sysbp_min,
                          d1_sysbp_noninvasive_max,
                          d1_sysbp_noninvasive_min,
                          d1_temp_max,d1_temp_min, h1_diasbp_max,
                          h1_diasbp_min,h1_diasbp_noninvasive_max,
                          h1_diasbp_noninvasive_min,
                          h1_heartrate_max,h1_heartrate_min,
                          h1_mbp_min,h1_mbp_max,h1_mbp_noninvasive_max,
                          h1_mbp_noninvasive_min,
                          h1_resprate_max,h1_resprate_min,
                          h1_spo2_max,h1_spo2_min,
                          h1_sysbp_max,h1_sysbp_min,
                          h1_sysbp_noninvasive_min,
                          h1_sysbp_noninvasive_max))
names(data)

```

## Delete Multicollinearity 
### singularities
```{r}
model_logit <- glm(hospital_death ~ .,family=binomial,data=data)
summary(model_logit)
```
ada attribute yang bernilai NA dikarenakan ada suatu Singularitas, atau kemungkinan ada suatu Multicollinearity

### Dikarenakan adanya singularitas, maka ada Multicolinnearity
```{r}
data <- data %>% select(-c(apache_2_bodysystem))
model_logit <- glm(hospital_death ~ .,family=binomial,data=data)
summary(model_logit)
```

### Dihapus Variable yang bernilai
```{r}
data <- data %>% select(-c(d1_sysbp_noninvasive,apache_3j_diagnosis,
                            d1_diasbp_noninvasive,d1_mbp_noninvasive,
                            h1_mbp_noninvasive,h1_diasbp_noninvasive))
model_logit <- glm(hospital_death ~ .,family=binomial,data=data)
summary(model_logit)

df_vif <- vif(model_logit)
df_vif <- as.data.frame(df_vif)

colnames(df_vif) <- c("GVIF","Df","VIF")
df_vif_fil <- df_vif %>% filter(VIF>=5)
df_vif <- df_vif %>% arrange(VIF)
df_vif
```

<<<<<<< HEAD
## Check data after Feature Selection
```{r}
summary(data)
```

## Balancing Class
```{r}
N_min <- min(unname(table(data$hospital_death)))
data <- ovun.sample(hospital_death ~ ., data=data,N=2*N_min ,seed=1234)$data

```

## Splitting Data
```{r}
set.seed(1234)
ind <- sample(2, nrow(data), replace = T, prob = c(0.8, 0.2))
trainData <- data[ind == 1,]
testData <- data[ind == 2,]
trainData
```

## Model Evaluation

### Training and Ploting error
```{r}


trainData_x <- trainData %>% select(-c(hospital_death))
trainData_y <- trainData$hospital_death

classifier_RF = randomForest(x = trainData_x,y = trainData_y)

#classifier_RF = train(x = trainData_x,y = trainData_y)
plot(classifier_RF)
```

### Plotting Variable Importance
```{r,out.width="60%",out.height="500%"}
varImpPlot(classifier_RF)
```


### Predict & Evaluation
```{r}
testData_x <- testData %>% select(-c(hospital_death))
testData_y <- testData %>% select(c(hospital_death))
testData_y <- testData_y$hospital_death

predict_y <- predict(classifier_RF,testData_x)
predict_y <- as.vector(predict_y)
predict_y <- factor(predict_y,levels = c("Survived","Death"))

# predict_y

confusionMatrix(predict_y,testData_y)
```


## Time Limit
```{r}
current_2 <- Sys.time()
deltatime_rpart <- current_2 - current_0
print("Time Modelling :")
print(deltatime_rpart)
```